Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-23 doc/JFLA2022/paper.tex
fix typos
fix more typos

 \begin{itemize}
   \item The game starts at an initial step $i\in\mathbb{N}$ (not necessarily $0$).
   \item  The hydra is always the the graphical representation of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form. For instance, Fig~\ref{fig:round}) shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.

@@

\begin{figure}[h]
  \centering
  \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$ for any natural number $i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$ for any $i \in \mathbb{N}$.
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(k)$ for any $i\in \mathbb{N}$.
\end{itemize}
\vspace{4pt}
\inputsnippets{HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}

>>>>

 \begin{itemize}
   \item The game starts at an initial step $i\in\mathbb{N}$ (not necessarily $0$).
   \item  The hydra is always the the graphical representation of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form. For instance, Fig~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.

@@

\begin{figure}[h]
 \noindent
 For any $i\in\mathbb{N}$,
   \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$.
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(i)$.
\end{itemize}
\vspace{4pt}
\inputsnippets{HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}
